\section*{Grading Criteria}

A standard grading scale with rounding at the 0.5\% mark will be used: A = 89.5\% or above; B = 79.5--89.4\%; C = 69.5--79.4\%; D = 59.5--69.4\%; E = below 59.5\%.

A total of 1405 points, not including bonus assignments, can be earned by the end of the semester after completing all assignments. The total points earned at the end of the semester is divided by 1405 to determine your final course grade.

\begin{tcolorbox}[
  enhanced,
  colback=blue!2,
  colframe=DeepBlue,
  boxrule=0.8pt,
  arc=3pt,
  left=10pt,
  right=10pt,
  top=8pt,
  bottom=8pt
]
{\bfseries\color{DeepBlue} Grade Scale}

\vspace{0.25em}

\textbf{A} --- To earn an A, students must have 1258 or more points. This is equivalent to 89.5\% or above.

\vspace{0.2em}

\textbf{B} --- To earn a B, students must have 1117 to 1257 points. This is equivalent to 79.5 to 89.4\%.

\vspace{0.2em}

\textbf{C} --- To earn a C, students must have 977 to 1116 points. This is equivalent to 69.5 to 79.4\%.

\vspace{0.2em}

\textbf{D} --- To earn a D, students must have 836 to 976 points. This is equivalent to 59.5 to 69.4\%.

\vspace{0.2em}

\textbf{E} --- To earn an E, students must earn 835 or fewer points. This is equivalent to below 59.5\%.
\end{tcolorbox}

\subsection*{Determining Your Grade Throughout the Semester}

After each major course deadline, you should evaluate your progress by dividing the total points you've earned on that date by the total number of points possible at that point in the course. This will give you a percentage score and allow you to determine your standing in the course. Please do NOT use the percentage provided in Blackboard alone as it may not always accurately reflect your grade. Please use the point information provided in the master course schedule and the assignment list in Blackboard to determine your grade at any time during the semester. \textbf{Email or call me at any time if you have questions about your grade.}

\section*{Attendance Statement}

Your attendance is determined by completion of assigned material. You are expected to access course materials online in Blackboard and check your KCTCS email account daily. You are responsible for all posted announcements, assignments, quizzes, and exams.

Because this is an accelerated 8-week online course, attendance begins with completion of the required Start Here assignments during the first week of class. Students who do not complete the required first-week attendance assignments may be dropped from the course without notification as per home campus procedures.

Additional assignments are due, on average, every 2--3 days at 11:59 p.m. eastern time. Case Study assignments are due at the end of each 3-chapter module. Each of the four Module Lecture and Lab Exams will be completed at the end of the corresponding 3-chapter module. See the course schedule in Blackboard for all official due dates.

\section*{Late Assignments and Make-Up Policy}

Assignments, lab activities, SmartBook assignments, and quizzes are due on the dates listed in the course schedule. Most assignments include an automatic two-day extension period beyond the original due date. Students may continue working during this extension period without contacting me.

After the late submission deadline has passed, the assignment will close and no additional submissions will be accepted. Because all students receive the same automatic extension opportunity, individual requests to reopen assignments are generally not granted.

Students are encouraged to complete assignments by the original due date whenever possible. The two-day extension period is intended to provide flexibility for unexpected events, scheduling conflicts, work obligations, and minor technical difficulties while helping students remain on pace with the course.

Module exams and final exams should be completed by the scheduled deadline. Students who miss a module exam may be eligible for one make-up exam opportunity near the end of the semester. Information regarding the make-up exam process will be provided during the final weeks of the course.

If a significant emergency or extended absence affects your ability to complete coursework, please contact me as soon as possible to discuss available options.