\section*{Withdrawal Policy}

A student may officially withdraw from any class up to and including the date of midterm with a W grade. After the date of midterm and through the last class of the semester or session, any student may officially request to withdraw from a course and receive a W, which may be given at the discretion of the instructor.

Withdrawal requests will only be approved if the student has continued working in class and at least 80\% of the coursework to that date is completed with a grade more than 0. An instructor shall not assign a student a W for a class unless the student has officially withdrawn from that class in a manner prescribed by the college. The grade of W may be assigned by the College Appeals Board in classes involving a violation of student academic rights or for academic offenses. Please refer to the Student Records Office for more information.


\section*{Academic Integrity}

Students must complete their own work. Academic dishonesty will not be tolerated. A first offense will result in a failing grade on the assignment. A second offense will result in a failing grade for the course.

Please refer to the SCC Student Code of Conduct for more information.

\section*{Accessibility Services for Students with Disabilities}

Somerset Community College strives to make learning experiences accessible to all participants and is committed to providing reasonable accommodation for all persons with disabilities. If you are seeking accommodations for this course under the Americans with Disabilities Act (ADA), you are required to contact the Accessibility/Disabilities Services Office.

To request accommodations, complete the Student Request for Services form. Please do not request accommodation directly from your instructor without a letter of accommodation from the Accessibility/Disability Services Office.

If you are a student from a KCTCS college other than Somerset Community College, contact your Home College for establishing disability accommodations. You can find your Home College's Accessibility/Disability Services Office contact information on the KCTCS Disability Services site. Your Home College will communicate with your instructors and Accessibility/Disability Services Office to provide you with reasonable and appropriate accommodation. Your accommodations will begin after the instructor has received confirmation of your accommodation from the Accessibility/Disability Services Office. Accommodation cannot be applied to your course retroactively.

\begin{tcolorbox}[coursetip]
{\bfseries Accessibility Services Contact Information}

\vspace{0.3em}

\renewcommand{\arraystretch}{1.1}
\begin{tabularx}{\linewidth}{@{}>{\bfseries}l X@{}}
Coordinator: & \textbf{Amanda Vanhook} \\
Email: & amanda.vanhook@kctcs.edu \\
Office Email: & SCC-Accessibility@kctcs.edu \\
Phone: & 606-451-6706 \\
Appointments: & In-person, virtual, and phone appointments available \\
Somerset Office: & Hal Rogers Student Commons Building, Office 116 \\
Laurel Office: & Building 3, Office 103B \\
\end{tabularx}

\end{tcolorbox}

\section*{Procedures Relating to Discrimination, Harassment, and Sexual Misconduct}

Students may direct complaints of discrimination or harassment to Dean of Student Affairs Tracy Casada at \\
\textbf{tracy.casada@kctcs.edu or 606-451-6631} for resolution pursuant to the Code of Student Conduct. Sexual misconduct matters should be directed to the Title IX Coordinator Tracy Casada to be handled in accordance with the Sexual Misconduct Procedure. Any responsible employee who receives information related to sexual misconduct is required to report it to the Title IX Coordinator. Please refer to the KCTCS Title IX procedures for more information.

\clearpage

\section*{Student Academic and Technical Support}

Somerset Community College offers support to all its students, whether enrolled in classes on campus or online. Your instructor is your primary resource, but the Learning Commons branches are available for assistance with research, tutoring, and computer services. Tutoring appointments can be made online but are not necessary. Walk-ins are welcome. Students can also access contact information and hours of operation for all the branches of the Learning Commons. For more information, call 606-451-6710.

\begin{tcolorbox}[coursetip]
{\bfseries Technical Support}

Blackboard technical support is available by telephone at 855-664-6722, option 4.
\end{tcolorbox}



\section*{Starfish}

SCC is dedicated to your academic success. Starfish is a program available to all students to enhance communication among students, instructors, and advisors. To access Starfish, just log in to Blackboard and click Starfish link. Ask your instructor or advisor for details. Check out SCC's website for more details and helpful instructions.

\section*{SNAP}

Safety Notification Alert Process (SNAP) is the official notification system for the Kentucky Community and Technical College System (KCTCS). SNAP alerts users to on-campus emergencies, including closures for inclement weather, for all 16 KCTCS colleges and the System office. With SNAP you can:

\begin{itemize}
\item Find out if classes are cancelled or delayed due to weather, power outages, or other unexpected events impacting campus.
\item Get severe weather notifications so you can take shelter when a storm hits.
\item Receive emergency messages when something or someone could be a threat to your personal safety.
\end{itemize}

Visit the KCTCS SNAP site to sign up and/or update your mobile and email information.

\section*{KCTCS/SCC Tobacco Free Policy}

``Tobacco use, including chewing (oral), smoking, and electronic cigarettes are not permitted on the properties of Somerset Community College campuses and centers, including buildings, sidewalks, and parking lots. KCTCS Tobacco Free Policy, Administrative Policies, Section 3.3.14.'' Please refer to the KCTCS Administrative Policies for additional information.

\section*{Additional Information}

The College must remain flexible to meet challenges that may include epidemics, pandemics, natural disasters, human-influenced disasters, and any and all threats to the College campus, students, employees, and surrounding communities. To ensure the safety and well-being of our constituencies, the College maintains the right to move classes temporarily or permanently to online, remote platforms; to a hybrid section that includes some face-to-face learning and some remote learning; or to a different campus, location, building, or time.

Additionally, the College reserves the right to institute plans or practices in the physical classroom/lab/activity spaces and common areas to protect students and employees. The College will attempt to make these changes as minimally disruptive as possible, but the College reserves the sole right to alter the particular type, place, or time for their classes.
